
\documentclass[12pt,a4paper]{report}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
    urlcolor=blue
}
%Cambiar los colores de blue a black para la impresion final

%\topmargin -1cm
%\textheight 24cm
%\oddsidemargin -0.5cm
%\textwidth 17cm

\begin{document}

%PRIMERA PAGINA: La portada
\input{Portada.tex}
\newpage

%SEGUNDA PAGINA: El certificado
\input{Legal.tex}
\newpage

%TERCERA PAGINA: Los resumenes
\input{Resumenes.tex}
\newpage

%INDICES
\tableofcontents
\listoffigures
\listoftables

\input{Intro.tex}
\input{ETA.tex}

\input{CAP1.tex}
\input{CAP2.tex}
\input{CAP3.tex}

\input{Conclusion.tex}

\begin{thebibliography}{99}

\bibitem{Abadie} A. Abadie, J. Gardeazabal, \textit{The economic costs of conflict: A case-control study for the Basque Country}, American Economic Review 93 (1) 113-132 (2003).
\bibitem{Colomb} J.A. Adam, J.A. Sokolowski, C.M. Banks, \textit{A two-population insurgency in Colombia: Quasi-predator-prey models-A trend towards simplicity}, Mathematical and Computer Modelling 49 (5-6) 1115 - 1126 (2009), doi: 10.1016/j.mcm.2008.03.017.
\bibitem{exilio2} J. Alcaide, Evoluci\'on de la poblaci\'on espa\~nola en el siglo XX, por provincias y comunidades aut\'onomas (Evolution of the Spanish population in the 20th century, by provinces anc autonomous communities), Fundaci\'on BBVA, 2007. 
\bibitem{Alonso} R. Alonso, F. Reinares, \textit{Terrorism, human rights and law enforcement in Spain}, In: Ranstorp, M. and Wilkison, P. (Eds.), Terrorism and human rights (2008).
\bibitem{Arney} C. Arney, \textit{Mathematical Modeling of "hearts and minds" in the Terrorism/Counter-Terrorism Struggle}, \url{http://jointmathematicsmeetings.org/meetings/national/jmm/1067-r1-237.pdf} (2010).
\bibitem{auto} Auto del Juzgado Central de Instrucci\'{o}n  n. 5, Madrid, de 26 de agosto de 2002. Sumario 25/02 Y (Central Court Order No. 5, August 25th 2002, Summary 25/02 Y).

\bibitem{BALI} V.A. Bali, \textit{Terror and elections: Lessons from Spain}, Electoral Studies 26 (3) 669 - 687 (2007), doi: 10.1016/j.electstud.2007.04.004.
\bibitem{libroF} H.T. Banks, C. Castillo-Ch\'{a}vez (Editors), Bioterrorism: Mathematical Modeling Applications in Homeland Security, in: SIAM Frontiers in Applied Mathematics, vol. 28, SIAM, Philadelphia (2003).
\bibitem{Barros2} C.P. Barros, \textit{An intervention analysis of terrorism: The Spanish ETA case}, Defence and Peace Economics 14 (6) 401-412 (2003).
\bibitem{Barros3} C.P. Barros, L.A., Gil-Alana, \textit{ETA: A persistence phenomenon}, Defence and Peace Economics 17 (2) 95-116 (2006).
\bibitem{BARROS} C.P. Barros, J.P. Passos, L.A. Gil-Alana, \textit{The timing of ETA terrorist attacks}, Journal of Policy Modeling 28 (3) 335 - 346 (2006), doi: 10.1016/j.jpolmod.2005.12.001.
\bibitem{GoodIdea} L.M.A. Bettencourt, A. Cintr\'{o}n-Arias, D.I. Kaiser, C. Castillo-Ch\'{a}vez, \textit{The power of a good idea: Quantitative modeling of the spread of ideas from epidemiological models}, Physica A: Statistical Mechanics and its Applications 364 $513-536$ (2006), 10.1016/j.physa.2005.08.083.
\bibitem{elecGen}  A. de Blas, J. Pastor (Eds.), Fundamentos de ciencia pol\'{\i}tica (Basics on political sciences), UNED (2001).
\bibitem{BLOWER} S.M. Blower, H. Dowlatabadi, \textit{Sensitivity and Uncertainty Analysis of Complex Models of Disease Transmission: and HIV Model, as an Example}, International Statistical Review 62 (2) 229-243 (1994).
\bibitem{Congreso} Bolet\'{\i}n Oficial de la Cortes Generales (Diary of the Spanish Parliament). Available at \url{http://www.congreso.es/public_oficiales/L8/CONG/BOCG/D/D_204.PDF}. 
\bibitem{Lbuesa} M. Buesa, \textit{ETA S.A. El dinero que mueve el terrorismo y los costes que genera} (ETA Inc. The money moved by terrorism and the generated cost), Ed. Planeta (2011).

\bibitem{Fanatismo} C. Castillo-Ch\'{a}vez, B. Song, \textit{Models for the transmission dynamics of fanatic behavior}, in: H.T. Banks, C. Castillo-Ch\'{a}vez (Eds.), Bioterrorism: Mathematical Modeling Applications in Homeland Security, in: SIAM Frontiers in Applied Mathematics, vol. 28, SIAM, Philadelphia, pp. $155-172$ (2003).
\bibitem{Benito} B.M. Chen-Charpentier, J.C. Cortes, J.V. Romero, M.D. Rosello, \textit{Some recommendations for applying gPC (generalized polynomial chaos) to modeling: An analysis through the Airy random differential equation}, Appl. Math. Comput. 219, 4208--4218 (2013), doi: 10.1016/j.amc.2012.11.007.
\bibitem{cherif} A. Cherif, H. Yoshioka, W. Ni, P. Bose, \textit{Terrorism: Mechanism of Radicalization Process, Control of Contagion and Counter-Terrorist Measures}, \url{http://arxiv.org/pdf/0910.5272.pdf} (2010).
\bibitem{bay} F.C. Coelho, C.T. Code\c{c}o, M.G.M. Gomes, A bayesian framework for parameter estimation in dynamical models, PLoS ONE 6(5):e19616 (2011), doi: 10.1371/journal.pone0019616.
\bibitem{ETA} Communiqu\'e of ETA January 8th 2011. Video published in GARA. Available at \url{http://www.gara.net/bideoak/110108_video/} (in Spanish).
\bibitem{almu}  J.C. Cortes, M. Ehrhardt, A. Sanchez-Sanchez, F.J. Santonja, R.J. Villanueva, \textit{Modelling the dynamics of the students academic performance in the German region of North Rhine-Westphalia: an epidemiological approach with uncertainty}, International Journal of Computer Mathematics (in press) (2013), doi: 10.1080/00207160.2013.813937.
\bibitem{CF} N.A. Christakis, J.H., Fowler, \textit{Connected: the surprising power of our social networks and how they shape our lives}. Brown and Company. Hachette Book Group. (2009).

\bibitem{Groot} M.H. DeGroot, \textit{Probability and Statistics}, Addison-Wesley, New York, 1986.
\bibitem{4trama} J.M. de Pablo, \textit{La cuarta trama. Verdades y mentiras en el caso del 11-M} (The 4th conspiracy. Trues and lies about 11-M), Ed. Ciudadela, (2009).
\bibitem{exilio3} Di\'aspora democr\'atica vasca (Basque democratic diaspora), Cuadernos de Ermua \url{http://www.foroermua.com/Cuadernos de Ermua 17.pdf} (in Spanish) 
\bibitem{Dogan} G. Dogan, \textit{Bootstrapping for confidence interval estimation and hypothesis for parameters of system dynamics models}, System Dynamics Review 23 (2007) 415--436.
\bibitem{Ldominguez} F. Dominguez, \textit{Dentro de ETA} (Inside ETA), Ed. Punto de lectura (2006).
\bibitem{Buesa} El libro negro de ETA (The black book of ETA) \url{http://www.libertaddigital.com/opinion/mikel-buesa/el-libro-negro-de-eta-68926/} (in Spanish)

\bibitem{Enders1} W. Enders, T. Sandler, \textit{Causality between transnational terrorism and tourism: The case of Spain}, Terrorism 14 (1) 49-58 (1991).
\bibitem{Enders2} W. Enders, T. Sandler, \textit{Terrorism and foreign direct investment in Spain and Greece}, Kyklos 49 (3) 331-352 (1996).
\bibitem{ceaseFire} ETA's delaration of cease-fire, Jan 8th, 2011 \url{http://www.elpais.com/elpaismedia/ultimahora/media/201101/10/espana/20110110elpepunac_1_Pes_PDF.pdf} (in Spanish)
\bibitem{eusko} Euskobarometro data series. Available at \url{http://www.ehu.es/euskobarometro/}.
\bibitem{euskoNOV2012} Euskobarometro report, \url{http://www.ehu.es/euskobarometro/index.php?option=com_content&view=article&id=152&Itemid=52}

\bibitem{FOURNIER} P.F. Fournier, R. Nadeau, A. Blais, E. Gidengil, N. Nevitte, \textit{Time-of-voting decision and susceptibility to campaign effects}, Electoral Studies 23 (4) 661 - 681 (2004), doi: 10.1016/j.electstud.2003.09.001.
\bibitem{Spanos} R. Ghanem, P. Spanos, \textit{Stochastic Finite Elements: A Spectral Approach}, Dover Publications, New York, (2003).
\bibitem{tabaco} F. Guerrero, F.J. Santonja, R.J. Villanueva, \textit{Analysing the Spanish smoke-free legislation of 2006: a new method to quantify its impact using a dynamic model}, International Journal of Drug Policy 22-4 (2011) 247-251.
\bibitem{Hair} J.F. Hair, R.E. Anderson, R.L. Tatham, W.C. Black, \textit{Multivariate Data Analysis}, Prentice-Hall, 2006.
\bibitem{Harmon} C.C. Harmon, \textit{Spain's ETA Terrorist Group is Dying}, Orbis, Volume 56, Issue 4 (2012) Pages 588-607, 10.1016/j.orbis.2012.08.005.

\bibitem{maitre} O.P. Le Maitre, O.M. Knio, \textit{Spectral Methods for Uncertainty Quantification}, Series Scientific Computation,  Springer, Netherlands (2010).
\bibitem{LP} Ley Org\' anica 6/2002 del 27 de junio (Organic Law 6/2002, of 27 Juny 2002). Available at \url{http://www.boe.es/boe/dias/2002/06/28/pdfs/A23600-23607.pdf}.
\bibitem{llera} F. Llera, \textit{ETA: Ej\'ercito secreto y movimiento social} (ETA: secret army and social movement) in Revista de Estudios Politicos (Nueva Epoca), no 78, p 161-193 (1992).

\bibitem{Martcheva} M. Martcheva, C. Castillo-Ch\'{a}vez, \textit{Diseases with chronic stage in a population with varying size}, Mathematical Biosciences 182 (2003) $1-25$.
\bibitem{exilio1} C. Mart\'{\i}nez, Los exilios vascos y el r\'egimen nacionalista (The exile of the Basques and the Nationalist regime) \url{http://www.abc.es/hemeroteca/historico-25-07-2002/abc/Nacional/los-exilios-vascos-y-el-regimen-nacionalista_116643.html} (in Spanish)
\bibitem{Wolfram} \textit{Mathematica} \url{http://www.wolfram.com/products/mathematica}
\bibitem{MCKAY} M. McKay, M. Meyer, \textit{Critique of and Limitations on the Use of Expert Judgements in Accident Consequence Uncertainty Analysis}, Radiation Protection Dosimetry 90 (3) (2000) 325-330.
\bibitem{Mena} J. Mena-Lorca, H.W. Hethcote, \textit{Dynamic models of infectious diseases as regulators of population sizes}, Journal of Mathematical Biology 30 (1992) $693-716 $.
\bibitem{MI} Ministerio del Interior (Spanish Ministry of Internal Affairs). Available at \url{http://www.mir.es/DGRIS/Terrorismo_de_ETA/ultimas_victimas/p12b-esp.htm}. 

\bibitem{Nelder} J. A. Nelder, R. Mead, \textit{A simplex method for function minimization}, Computer Journal 7 (1964), 308--313, doi: 10.1093/comjnl/7.2.155.
\bibitem{OLSSON}  A. Olsson, G. Sandberg, O. Dahlblom, \textit{On Latin hypercube sampling for structural reliability analysis}, Structural Safety 25 (1) (2003) 47 - 68, doi: 10.1016/S0167-4730(02)00039-5.

\bibitem{miguel} M. Peco, \textit{Aproximacion funcional a los movimientos radicales en el ejercicio de la violencia politica} politica (A Functional Approach to Radical Movements Engaged in Political Violence), Ph.D. Dissertation, UNED (2011)
\bibitem{Lmiguel} M. Peco, L. Peral, \textit{El conflicto de Colombia} (The conflict of Colombia), Instituto de Estudios Internacionales y Europeos "Francisco de Vitoria", (2006).
\bibitem{NOS} M. Peco, F.-J. Santonja, A.-C. Tarazona, R.-J. Villanueva, J. Villanueva-Oller, Effect of the Spanish Law of Political Parties (LPP) on the attitude of the Basque Country population towards ETA: A dynamic modelling approach, Math.  Comput. Modell. 57 (2013) 1679--1685, doi:10.1016/j.mcm.2011.11.007.
\bibitem{PC} Posici\'{o}n Com\'{u}n 2003/482/PESC del Consejo, de 27 de junio de 2003, por la que se actualiza la Posici\'{o}n Com\'{u}n 2001/931/PESC sobre la aplicaci\'{o}n de medidas espec\'{i}ficas de lucha contra el terrorismo y se deroga la Posici\'{o}n Com\'{u}n 2003/402/PESC. (Common Position 2003/482/PESC where the Common Position 2001/931/PESC about the application of specific measures against terrorism has been updated and Common Position 2003/402/PESC is revoked).
\bibitem{Press} W.H. Press, B.P. Flannery, S.A. Teukolsky, W. Vetterling, Numerical Recipes: The Art of Scientific Computing, Cambridge University Press, New York (1986).

\bibitem{Lreinares} F. Reinares, \textit{Patriotas de la muerte. Por qu\'e han militado en ETA y cu\'ando abandonan} (Patriots of death. Why they militated in ETA and when they abandon), Ed. Taurus, Madrid (2011).

\bibitem{Jairo} J. Santillana, \textit{A mathematical model of terrorism}, DRU Workshop 2011 Presentations, Disaster Resistant University Workshop: Building Partnerships in Mitigation, \url{http://scholarworks.uno.edu/dru2011/34}, (2011).
\bibitem{Jairo0} J. Santillana, \textit{A system of Stochastic Difference Equations Modeling Terrorism}, \url{http://jointmathematicsmeetings.org/meetings/national/jmm/1067-39-2089.pdf} (2000).
\bibitem{NOS1} F.J. Santonja, A.C.Tarazona, R.J. Villanueva, \textit{A mathematical model of the pressure of an extreme ideology on a society}, Comput. Math. Appl., 56 3, pp. 836-846 (2008).
\bibitem{sentencia} Sentencia de la Sala Especial (Art\'{i}culo 61 L.O.P.J.) del Tribunal Supremo, autos acumulados n. 6/2002 y 7/2002. (Sentence of the Especial Courtroom of the Supreme Court, Article 61 of the Law of Political Parties, accumulated court orders No. 6/2002 and 7/2002).
\bibitem{SNYDER} L.B. Snyder, \textit{Health Communication Campaigns and Their Impact on Behavior}, Journal of Nutrition Education and Behavior 39 (2, Supplement 1) (2007) S32 - S40, doi: 10.1016/j.jneb.2006.09.004.
\bibitem{stauffer1} D. Stauffer, M., Sahimi, \textit{Discrete simulation of the dynamics of spread of extreme opinions in a society}, Physica A: Statistical Mechanics and its Applications 364, 537 - 543 (2006), doi: 10.1016/j.physa.2005.08.040.
\bibitem{stauffer2} D. Stauffer, M., Sahimi, \textit{Can a few fanatics influence the opinion of a large segment of a society?}, The European Physical Journal B - Condensed Matter and Complex Systems 57, 147 - 152 (2007), doi: 10.1140/epjb/e2007-00106-7.

\bibitem{WEISBERG} H.F. Weisberg, \textit{Nonlinear models of electoral change: the implications of political time and chaos theory for the study of mass political behavior}, Electoral Studies 17 (3) (1998) 369 - 382, doi: 10.1016/S0261-3794(98)00033-X.
\bibitem{Xiu} D. Xiu, \textit{Numerical Methods for Stochastic Computations: A Spectral Method Approach}, Princeton University Press, New Jersey (2010).

\bibitem{mir} \url{http://www.infoelectoral.mir.es/min/} (in Spanish)

\bibitem{PaisVasco} \url{http://en.wikipedia.org/wiki/Basque_Country_(autonomous_community)}
\bibitem{demogPV} \url{http://www.eustat.es/} (in Spanish)
\bibitem{ev2012} \url{http://www.euskadi.net/q93TodoWar/eleccionesJSP/q93Contenedor.jsp?idioma=c&menu=li_2_1_1&opcion=menu} (in Spanish)

\bibitem{wETA} \url{http://en.wikipedia.org/wiki/ETA}

\bibitem{debil1} \url{http://www.20minutos.es/noticia/856404/0/rubalcaba/eta/debil/} (in Spanish)
\bibitem{debil2} \url{http://www.libertaddigital.com/nacional/2011-06-12/rubalcaba-bildu-tendria-menos-alcaldias-si-se-hubiera-hecho-de-otra-manera-1276426370/} (in Spanish)
\bibitem{debil3} \url{http://www.libertaddigital.com/nacional/camacho-dice-que-estamos-ganando-la-batalla-a-eta-que-esta-mas-debil-que-nunca-1276339356/} (in Spanish)

\bibitem{obstaculo} \url{http://www.bbc.co.uk/mundo/internacional/2010/09/100906_eta_razones_analisis_aw.shtml} (in Spanish)

\bibitem{MABlanco1} \url{http://www.fmiguelangelblanco.es} (in Spanish)
\bibitem{MABlanco2} \url{http://en.wikipedia.org/wiki/Miguel_Angel_Blanco}
\bibitem{MABlanco3} \url{http://www.elmundo.es/especiales/2007/07/espana/losmartiresdel97/album/mablanco/album_mablanco.html} (in Spanish)

\bibitem{OLara1} \url{http://es.wikipedia.org/wiki/Jose_Antonio_Ortega_Lara} (in Spanish)
\bibitem{OLara2} \url{http://www.elmundo.es/especiales/2007/07/espana/losmartiresdel97/album/olara/album_olara.html} (in Spanish)

\bibitem{11m} \url{https://en.wikipedia.org/wiki/2004_Madrid_train_bombings}

\bibitem{scaling} \url{http://scaling.imm.upv.es}

\end{thebibliography}

\end{document}
